R Notebook

### 2021-06-27 Exemples and Implementations.Rmd
Recenti modifiche con Optimal kernel SV

```{r include=FALSE}
#Calcolo intevalli di credibilità
#--------------------------------
CredInt<-function(fun){

@@

```{r}
Comparethetwo<-matrix(NA,nrow=2,ncol=2)
colnames(Comparethetwo)<-c("Credible Interval","RMSE")
rownames(Comparethetwo)<-c("transition","more efficient")
Comparethetwo[1,1]<-CredInt(pf1)
Comparethetwo[2,1]<-CredInt(pf2)
Comparethetwo[1,2]<-RMSE(truex,Filtervalues(pf1)$mean)
Comparethetwo[2,2]<-RMSE(truex,Filtervalues(pf2)$mean)
```

>>>>

```{r include=FALSE}
#Calcolo intevalli di credibilità
#--------------------------------
Coverage<-function(fun){

@@

```{r}
Comparethetwo<-matrix(NA,nrow=2,ncol=2)
colnames(Comparethetwo)<-c("Coverage","RMSE")
rownames(Comparethetwo)<-c("transition","more efficient")
Comparethetwo[1,1]<-Coverage(pf1)
Comparethetwo[2,1]<-Coverage(pf2)
Comparethetwo[1,2]<-RMSE(truex,Filtervalues(pf1)$mean)
Comparethetwo[2,2]<-RMSE(truex,Filtervalues(pf2)$mean)
```
